Developing Software Center Using Evolutionary Prototyping Based-on HTML5

### 2014-04-30 Latex/Paper_format.tex
mulai ngisi konten paper

%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Bare Demo of IEEEtran.cls for Conferences}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Michael Shell}
\IEEEauthorblockA{School of Electrical and\\Computer Engineering\\
Georgia Institute of Technology\\
Atlanta, Georgia 30332--0250\\
Email: http://www.michaelshell.org/contact.html}
\and
\IEEEauthorblockN{Homer Simpson}
\IEEEauthorblockA{Twentieth Century Fox\\
Springfield, USA\\
Email: homer@thesimpsons.com}
\and
\IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
\IEEEauthorblockA{Starfleet Academy\\
San Francisco, California 96678-2391\\
Telephone: (800) 555--1212\\
Fax: (888) 555--1212}}

@@

\section{Introduction}
% no \IEEEPARstart
This demo file is intended to serve as a ``starter file''
for IEEE conference papers produced under \LaTeX\ using
IEEEtran.cls version 1.7 and later.
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
I wish you the best of success.

\hfill mds

\hfill January 11, 2007

\subsection{Subsection Heading Here}
Subsection text here.

\subsubsection{Subsubsection Heading Here}
Subsubsection text here.

@@

% use section* for acknowledgement
\section*{Acknowledgment}

The authors would like to thank...

@@

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{1}

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

>>>>

%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Developing Software Center Using Evolutionary Prototyping Based-on HTML5}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Imam Riadi}
\IEEEauthorblockA{Information Systems Study Program, Faculty of\\
Mathematics and Natural Sciences,\\
Ahmad Dahlan University, Yogyakarta, Indonesia}
\and
\IEEEauthorblockN{Estu Fardani}
\IEEEauthorblockA{Informatics Department, Science and Technology Faculty,\\
Sunan Kalijaga State Islamic University,\\
Yogyakarta, Indonesia}}

@@

\section{Introduction}
% no \IEEEPARstart
Software Center is software to manage application in a operating system such as install, delete or upgrade applications. It is a required software in all operating system, both conventional or mobile devices. BlankOn as the Indonesian local operating system should have this application but in reality this application is not yet available [1].

Traditionally, to do package management, user deal with installing package form console with apt syntac. This way is worst to other people. In other way user can use Synaptic Package Manager, a simple software center. But this interface just to old style.

HTML5 is a trend of programming because this technology easy to adapted, can run in multple platfrom up to desktop utilization [2].

This research tries to make software center HMTL5-based as solution for BlankOn.
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
\section{Software Center}

YaST (yet another setup tool)
Software center for opensuse. It use to manage all of user need for use opensuse. Example to install application, package, network setting etc. YaST devel form ruby and YCP and qt for UI, base c++[3 yast vendor].

scr uset to injek scrip. interface base on qt.

Ubuntu Software Center
Software manajemen for ubuntu by canonical. It is free software written in Python, PyGTK/PyGObject based on GTK+ and the further development of the GNOME application, gnome-app-install. base commant for apt manajemen.[4][5]

\section{HTML5 App in desktop}
run html 5 on dektop need other program, suck webkit to rendering html 5.

\subsection{Webkit}
webkit is renderin page to run html5, it base bla
figure 1 how webkit work

\subsection{WarSi}
WarSi (Warung aplikasi)
gui from apt command
how it work.
firgure 2.

\section{Development WarSi}
\subsection{Development Method}
Developmen use evoluitionary protoyiping,
- because (alasan) [7]
figure 3 how prototyping

\subsubsection{Initial Consep and requirment}
what konsep

\subsubsection{Quick Desain}

\subsubsection{Build Prototype}

\subsubsection{Costumer Evaluation, Update}

\subsubsection{If not done yet, Refine design and prototype}

\subsubsection{IF happy, final testing and produck release}

\subsection{UML (Unified Modele Language}

\subsubsection{Use Case Diagram}
as figure 4
thi app have 2 main requrment

\subsubsection{Activity Diagram}
- a
- b

\subsubsection{Squence Diagram}
(need redraw)

\subsection{Result Develop}

\subsection{Testing}
blackbox model
for same hasil (diagram pie)

@@

% use section* for acknowledgement
\section*{Acknowledgment}
Thank you to Ahmad Dahlan University for funding this research

@@

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}
{1}
% \bibitem{IEEEhowto:kopka}
% H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\bibitem{IEEEhowto:kopka}
Duncan Mac-Vicar P., \emph{What you should know about YaST}, Novell, Inc, 2008.

\bibitem{IEEEhowto:kopka}
Mathew Paul Thomas, \emph{Ubuntu Software Center}, http://wiki.ubuntu.com/SoftwareCenter.

\bibitem{IEEEhowto:kopka}
Lounpad Ubuntu

\bibitem{IEEEhowto:kopka}
Wiki BlankOn,

\bibitem{IEEEhowto:kopka}
John Dooley, \emph{Software Development and Professional Practice}, Springer Science Business Media, Inc, 2011.
